---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# GeneseeBulk

<!-- badges: start -->
<!-- badges: end -->

The goal of GeneseeBulk is to facilitate analysis (differential expression) of Bulk RNASeq.

## Installation

You can install the development version of GeneseeBulk from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("amcdavid/GeneseeBulk")
```

## Example

The Genesee* family of packages is organized around project templates that copy 
over various parametrized markdown scripts.  
As such, there's some code required to set
overall parameters for the project.
```{r example}
library(GeneseeBulk)
dir.create(tmp <- tempfile())
proj_directory = Genesee::genesee_skeleton(genesee_root = tmp,
                          investigator = 'Plato', 
                          project_title = 'Crito',
                          project_type = 'RNA',
                          init_git = FALSE)
```

After that, you would edit `00driver.R` to customize how the markdown are run.
```{r, file = file.path(proj_directory, '00driver.R'), echo = 3:21, eval = FALSE}

```

### Templates

At the moment, there are `r length(list.files(proj_directory, pattern = '*.Rmd'))` 
template available:
```{r}
list.files(proj_directory, pattern = '*.Rmd')
```

